A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma

### 2021-03-16 main.tex
{fig:figure5}

*** make Figure 5 holistic:
%meridian and emotion has mutual reaction
%meridian effect tissue and organ
%(autonomic nerve system, myofascial network, prefrontal cortex)
%placebo-effect influence on drug discovery
%gene expression in deep learning
%Ching, T. et al. Opportunities and obstacles for deep learning in biology and medicine. J. R. Soc. Interface 15, (2018).
%慈悲心 利他心
%博士班學生，越研究越發現，科學的不足，心理與靈性的力量，更是背後推動的冥冥力量，身心靈是合一的
%#正念 除了可以減壓，還可以治癒疼痛
%Environment 改造患者的心，就能改造他的身體環境，有利消除癌症

>>>>

%*** make Figure 5 holistic: Figure_5_holisticCare.pdf
\begin{figure}[hp]
\centering
\includegraphics[width=14cm]{Figure_5_holisticCare.pdf}
\bcaption{The concept of holistic care for \acrshort{hnscc} patients.}
{
[Carcinogenesis] Under the mind-brain-body axis, a stressful environment will trigger the emotional reception. The subconscious mind (brain) will release stress hormones and inflammation signals in response to the emotion. The inner environment of physical body (cells) alter epigenetic control in terms of gene regulation and mRNA expression. In a long time of incubation, the tissue/cells will be transformed into dysplasia then malignancy.\\
[Cancer care] Holistic care should take care of spiritual, emotional, physical and socioeconomic needs of cancer patients. Physical care will be carried out by medication therapy or surgery. After establishment of therapeutic relationship, the physicians' spiritual properties (empathy, sympathy, and compassion) will engage their patients and recovery their self-compassion to gain the resilience against the disease.
[Suggested health care record] Beside physical, pathological, or psychological data, electric healthcare record (EHR) and \acrshort{tcga} should collect "holistic features".
}
\label{fig:figure5}
\end{figure}
%meridian and emotion has mutual reaction
%meridian effect tissue and organ
%(autonomic nerve system, myofascial network, prefrontal cortex)
%placebo-effect influence on drug discovery
%gene expression in deep learning
%Ching, T. et al. Opportunities and obstacles for deep learning in biology and medicine. J. R. Soc. Interface 15, (2018).
%慈悲心 利他心
%博士班學生，越研究越發現，科學的不足，心理與靈性的力量，更是背後推動的冥冥力量，身心靈是合一的
%#正念 除了可以減壓，還可以治癒疼痛
% modify the dark environment 改造患者的心，就能改造他的身體環境，有利消除癌症
